### 2020-05-06 writeup/intro.tex
edits

The idea of transferring information across tasks has recently found applications in lots of work in deep learning.
In our own experience as well as discussions with collaborators, we have often heard that multi-task learning that is applied on heterogeneous data often result in suboptimal models (or negative transfer in more technical terms).

To gain insight into the working of these methods, we consider a principled study of how hard parameter sharing based multi-task and transfer learning works for learning multiple high-dimensional linear regression tasks.
We follow the model proposed in \cite{WZR20} that to identify conditions on when multi-task and transfer learning works, and when it doesn't.
We refine the task covariance part of \cite{WZR20} into three factors: model distance, covariate shift matrix and data ratio \cite{PY09,K18}.
We study a high-dimensional linear regression setting where the target task data size is limited.

\smallskip
\noindent\textbf{Setup.} We are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
We shall assume that each task data follows a linear model.
For every $1\le i\le k$, we assume that
\[ Y_i = X_i \beta_i + \varepsilon_i, \]
where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
We assume that for every row $x$ of $X_i$, we have
\[ \ex{xx^{\top}} = \Sigma_i. \]
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.

We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.
The shared body $B$ plays an important role because it allows information transfer between different task data.
This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.

%We formulate the heterogeneity between different task data under covariate and model shifts .
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
\todo{list those here}
These are achieved through tight generalization bounds established in the high-dimensional regression setting.
Our main results are described as follows.

\smallskip
\noindent{\bf Variance reduction from information transfer.}
	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
	We show that multi-task learning helps improve performance over target tasks by \textit{reducing variance} through newly added source task data.
	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
	We show upper and lower bounds on both the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.

	{\it Insight 1: MTL vs STL.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
	In particular, if model shift is too large, we get negative transfer from multi-task training.

	{\it Insight 2: TL vs MTL.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
		The amount of improvement becomes more significant as the model distance becomes larger.

	We show the result for two settings: 2 tasks with different covariates, and $k$ tasks that all share the same covariates.
	The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
	We show that our results and insights from the above can be extended to this setting as well.

	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]

@@

\smallskip
	\noindent\textbf{Covariate shift and data ratio.}
	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
	We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.

	\textit{Insight 3: TL vs STL.} When data ratio is small, having complementary covariance matrices is better. When data ratio is large, having the same covariance matrix is better.

>>>>

Methods that can transfer the information from one task to help other tasks have recently found many applications in computer vision, natural language processing and reinforcement learning.
In our own experience as well as discussions with collaborators, we have often observed that multi-task learning that is applied on heterogeneous data often result in suboptimal models (or negative transfer in more technical terms).

To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
A typical process to do multi-task learning involves two steps:
(i) Jointly learn a shared representation for all the tasks;
(ii) Fine-tune the learnt model on a specific target task.
We focus on a hard parameter sharing model proposed in \cite{WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
The high-dimensional linear regression setting where the target task data size is limited captures the intuition that the target task only contains limited labeled data.

Concretely, our input consists of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
We use a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.
The shared body $B$ plays an important role because it allows information transfer between different task data.
This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.

We focus on comparing the test performance on a target task using estimators from doing multi-task training and transfer learning.
We compare the test performance of these estimators to the single-task baseline.
The details are described in Algorithm \ref{alg_estimator}.

%We formulate the heterogeneity between different task data under covariate and model shifts .
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
\todo{list those here}
We refine the task covariance part of \cite{WZR20} into three factors: model distance, covariate shift matrix and data ratio \cite{PY09,K18}.
These are achieved through tight generalization bounds established in the high-dimensional regression setting.
Our main results are described as follows.

\begin{algorithm}[!t]
	\caption{Multi-task learning using a hard-parameter sharing architecture}
	\label{alg_estimator}
	\begin{algorithmic}[1]
		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
		\State Training the shared body $B$.
		\State Optimizing the task heads on the validation set

		\begin{itemize}
			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
		\end{itemize}
		\State Problem statement: how can we compare the test error of the three estimators on the target task?
		%, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$?
	\end{algorithmic}
\end{algorithm}

\smallskip
\noindent{\bf Variance reduction from information transfer.}
	We show that the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
	We derive this result for the setting of two tasks with general inputs and $k$ tasks with the same covariates for any $k \ge 2$.
	The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
%	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
	We show bounds on the trade-off between the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.

	{\it Insight 1}: $\hat{\beta}_t^{\MTL}$ vs $\hat{\beta}_t^{\STL}$.
	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
	In particular, if model shift is too large, we get negative transfer from multi-task training.

	{\it Insight 2}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\MTL}$.
	Finally, we show that the transfer learning estimator always improves over mutli-task training.
	The amount of improvement becomes more significant as the model distance becomes larger.

%	We show the result for two settings: 2 tasks with different covariates, and $k$ tasks that all share the same covariates.
%	We show that our results and insights from the above can be extended to this setting as well.
	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]

@@

\smallskip
	\noindent\textbf{Covariate shift and data ratio.}
	For the case of two tasks with general inputs, we further study the factors that determine the transfer rate.
	We identify two factors, the covariate shift matrix and the ratio between number of task data.
%	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
%	We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.

	\textit{Insight 3}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\STL}$.
	Our result has implications on the following question.
	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices.
	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.

### 2020-05-06 writeup/proof_sketch.tex
edits

>>>>

\todo{these calculation goes to appendix}
\paragraph{The case of two tasks.}
From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
Here, equation \eqref{eq_mtl} simplifies to the following
\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
\begin{align*}
	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
\end{align*}
where we denote $w = w_1 / w_2$.
As a remark, when $w = 1$, we recover the linear regression estimator.

\medskip
\noindent\textit{Jointly optimizing over both tasks.}
Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
\begin{align}
		&\val(\hat{B}; w_1, w_2) \nonumber\\
	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
\end{align}
Minimizing the above loss is akin to performing multi-task training in practice.
Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.

\medskip
\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
\begin{align}
	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
\end{align}
In the above, the first is a bias term introduced by the model shift between the source and target tasks.
The second is a variance term, which decreases monotonically as we add more and more source task data.
Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.

There are two reasons for studying this setting.
First, this is akin to performing transfer learning using the hard parameter sharing architecture.
Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
The baseline where we solve the target task with its own data is
\begin{align*}
	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
\end{align*}
Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.

\todo{connect here}

### 2020-05-06 writeup/setup.tex
reorg intro setup
edits

\section{Preliminaries}

\paragraph{Generalization error.}
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on the test error for the target task:
%\begin{itemize}
%	\item Estimation error for the target model $\beta_t$: we consider their distance
%		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
		\begin{align*}
			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
		\end{align*}
%\end{itemize}

@@

%\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
%We remove the assumption that the models are the same.
%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
%\begin{align}
%	Y_i = X_i \beta_i + \varepsilon_i.
%\end{align}
%\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
%A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
%\begin{align}
%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
%\Sigma_i
%\end{align}

@@

\paragraph{The case of two tasks.}
From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
Here, equation \eqref{eq_mtl} simplifies to the following
\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
\begin{align*}
	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
\end{align*}
where we denote $w = w_1 / w_2$.
As a remark, when $w = 1$, we recover the linear regression estimator.

\medskip
\noindent\textit{Jointly optimizing over both tasks.}
Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
\begin{align}
		&\val(\hat{B}; w_1, w_2) \nonumber\\
	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
\end{align}
Minimizing the above loss is akin to performing multi-task training in practice.
Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.

\medskip
\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
\begin{align}
	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
\end{align}
In the above, the first is a bias term introduced by the model shift between the source and target tasks.
The second is a variance term, which decreases monotonically as we add more and more source task data.
Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.

There are two reasons for studying this setting.
First, this is akin to performing transfer learning using the hard parameter sharing architecture.
Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
The baseline where we solve the target task with its own data is
\begin{align*}
	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
\end{align*}
Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.

>>>>

\subsection{Setup and Main Results}\label{sec_setup}

We assume that for every row $x$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on the test error for the target task:
%\begin{itemize}
%	\item Estimation error for the target model $\beta_t$: we consider their distance
%		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
		\begin{align*}
			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
		\end{align*}
%\end{itemize}

\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}

@@

@@
